Building a framework to perform automated verification of solar photovoltaic off-grid systems

### 2018-11-01 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r1.tex
updated journal text

\section{Introduction}
% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps.
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by the IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
% 
% Here we have the typical use of a "T" for an initial drop letter
% and "HIS" in caps to complete the first word.
\IEEEPARstart{A}{ccording} to Coelho et al. \cite{Coelho}, there are presently 1.3 billion people with no access to electricity worldwide. 
%The definition of energy access usually includes both electricity access and access to modern fuels for cooking and heating, in order to replace traditional biomass. 
%Increased access to energy allows economic growth and poverty alleviation \cite{Karekesi}. 
%
%Among the options of renewable sources, there are hydro, wind, and solar photovoltaic (PV). 
Only a niche market a few years ago, solar photovoltaic (PV) are now becoming a mainstream electricity provider.
% changing the way the world is powered. 
Based on data from \cite{EPIA}, there was an increase of approximately 50\% from 2016 to 2017 in terms of new installations of PV. 
%The use of the power generation technology with renewable energy source is developing rapidly due to the industrial development \cite{Yatimi}. 
%The renewable energy leads to an advance all over the world by protecting the environment: it is clean,
%(low greenhouse gases emissions)
%operating silently, long lifetime, low maintenance, absence of fuel cost and inexhaustible \cite{Noroozian}. 
%Renewable energy, and particularly the power generation from solar energy using photovoltaic (PV) panels, has emerged as an alternative to fossil or nuclear fuel generation.
% 
%The PV cell in a solar photovoltaic system, as defined in \cite{Rawat}, is a semiconductor device, which directly converts the solar radiation into electrical energy. 
%
%Apart from PV modules; the 
%PV systems consist of PV modules, battery bank, controller, and inverter, plus the load. %Moreover, the optimum sizing of these devices is important for reliable operation.
%Therefore, these systems need to be designed properly according to the site, land area available, load requirement, load pattern, environmental conditions and economics in order to utilize available resources efficiently and economically \cite{Rawat}. %Furthermore, there is the need for proper modeling and simulation tools for people involved in their application. 
In order to validate or even simulate a potential PV solution, there are a myriad of tools available at the market, as RETScreen, HOMER, PVWatts, SAM, and Hybrid2.

%The increase in a number of PV systems installed all over the world brings the need for proper modeling and simulation tools for researcher and practitioners involved in their application. In order to validate or even simulate a potential PV solution, there are a myriad of tools. 
%However, to the best of our knowledge, this work can be the first work to perform automated verification of a solar PV off-grid project solution.  
%
%According to \cite{SEIA} and \cite{Chauhan}, solar is the most abundant source of renewable energy on earth. In SPV system, solar radiations are captured from the sun and turned into electricity using SPV cells made of silicon and other materials. SPV...
%
%In order to address different aspects of a SPV project, there is a myriad of public domain and commercial software available. According to \cite{Brooks}, the capabilities of these tools range from simple solar resource and energy production estimative, to site survey and system design tools, to complex financial analysis software (with optimization). Some tools also provide support to rebate programs applications and tax incentives (specific to each country or region), while other programs and worksheets focus on the technical aspects of system sizing and design.

%Manufactures and integrators have yet their proprietary software to perform various system sizing, with the drawback of include just their own products among the possibilities of choice, what restrict the solution.

%PV systems can be classified into grid-connected and stand-alone systems. At this proposal, only off-grid or stand-alone systems will be considered. The utilization of solar energy in off-grid mode has the potential to meet the energy need for remote rural areas of developing countries.

However, those tools are based in simulation models to validate a PV system. The use of simulation for verification is problematic, because is necessary to ensure the complete coverage of operating conditions, scenarios, and system inputs.

Formal methods based on model checking offer great potential to obtain a more effective and faster verification in the design process. Programs may be viewed as mathematical objects. 
%with behavior that is, in principle, well determined. 
 This makes it possible to specify systems as programs using mathematical logic, which constitutes the intended (correct) behavior. Then, one can try to give a formal proof or otherwise establish that the program meets its specification.%, as defined by \cite{Trindade}. 
%
%This area of research is referred as formal methods. % as defined in \cite{Clarkeetal}.
% Their aim is to establish system correctness with mathematical rigor. 
%In the recent decades, research in formal methods has led to the development of very promising verification techniques.
% that facilitate the early detection of bugs in order to ensure the correctness of the system. 
%
%Model-based verification techniques are based on models that describe the possible system behavior in a mathematically precise and unambiguous manner. 
%Thus, such problems as incompleteness, ambiguities, and inconsistencies, which normally are discovered only in later stages of the design, can be detected in advance, as described by \cite{Trindade}. 
Algorithms can verify the system model through systematically explore all their states.

@@

The results prove that the framework is more efficient in different case studies to found not proper functioning of PV systems than simulation with off-the-sheld tool. To the best of our knowledge, this is the first work to use a
%n SMT-based 
verification tool to solve this kind of problem. That is the main contribution of this paper.

@@

\section{Solar Photovoltaic System }
%According to \cite{Roy}, a 
A PV system is designed to give the electric supply to a load. This load can be either Alternate Current (AC) type or Direct Current (DC) type. Electric supply can be needed either in daytime or evening time. 
%(in particular cases, in both times). %The most basic PV system can give supply only in daytime.  
For night hours or rainy days, one needed to have batteries, where power can be stored and used.% \cite{Gules}.

@@

\section{Design and Validation of a Solar photovoltaic system}
%The design and validation of a PV system can be done by hand or with the aid of a software tool. 
%
In order to address different aspects of project system and systems design, there is a myriad of tools. 
%public domain and commercial software available for the PV market. 
%According to \cite{Brooks}, t
The capabilities of these tools range from simple solar resource and energy production estimation, %to site survey and system design tools,
 to complex financial analysis software (with optimization). 
%Some tools also provide support to rebate programs applications and tax incentives (specific to each country or region), while other programs and worksheets focus on the technical aspects of system sizing and design.
%
%Manufacturers and integrators have yet their proprietary software to perform inverter string sizing and various system sizing and design tools, with the drawback to just include their own products among the possibilities of choice. 
In this work, were evaluated the most popular tools, as PVWatts, SAM, Homer Pro, RETScreen Expert, and Hybrid2.

@@

\subsection{Paper Proposal x Reference Tools}
Considering the focus of this paper, only HOMER and RETScreen remain for comparative. All tools need some parameters inherently from manufacturer's catalog in order to size the system.
%, so the project starts with manufacturers and integrators tool to define the basic items of the project: panels, inverters, controllers, and batteries. 
After that, the potential solution is analyzed in another tool to validate or even optimize the solution. Therefore, that is the challenge of this work, i.e., to prove that is possible to use automated verification to validate an off-grid PV solution and to prove that this verification is more efficient and complete than the listed-more common tools.

The comparative between the Homer Pro and the automated verification tool is presented at the Section \ref{sec:results}.

\section{Component models for stand-alone PV system }
%The main purpose of this section is to describe the models for the elements of a standalone PV system: PV generator, battery, controller, inverter, and load. 
The modeling of the PV system is based on modular blocks, as illustrated in Fig.\ref{fig:blockdiagram}, from \cite{Hansen}. The modular structure facilitates the modeling of the other system structures and replacing of elements as, for instance, a DC load instead of an AC load.

@@

Where $ T_{air} $ is the ambient temperature, $NOCT$ is the nominal operating cell temperature (in $^{o}$C) that is found at the PV manufacturer's data-sheet, and $G$ is the solar irradiance ($ W/m^{2} $) of the place where the PV system is deployed.

@@

In \cite{Mellit} was established that the controller allows the management of energy between the load and the battery. The input signals for regulator model are the battery current ($ I_{br} $), PV generator's voltage ($ V_{PV} $), PV generator's current ($ I_{PV} $), and battery voltage ($ V_{b} $). The outputs are battery ($ I_{rb} $) current and used current ($ I_{u} $).

According \cite{Hansen}, to protect the battery against an excessive charge, the PV arrays are disconnected from the system, when the terminal voltage increases above a certain threshold $ V_{max \textunderscore off} $ and when the current required by the load is less than the current delivered by the PV arrays. PV arrays are connected again when the terminal voltage decreases below a certain value $ V_{max \textunderscore on} $. 
%This can be done by using a switch with a hysteresis cycle, as illustrated in Fig. \ref{fig:controllerover}. 
%
%\begin{figure}[h]
%\includegraphics[width=0.4\textwidth]{controllerover}
%\centering
%\caption{Operating principle of an overcharge protector (Source: \cite{Hansen})}
%\label{fig:controllerover}
%\end{figure}

To protect the battery against excessive discharge, the load is disconnected when the terminal voltage falls below a certain threshold $ V_{min \textunderscore off} $ and when the current required by the load is larger than the current delivered by the PV arrays \cite{Hansen}. The load is reconnected to the system, when the terminal voltage is above a certain value $ V_{min \textunderscore on} $.
%, using a switch with a hysteresis cycle, as shown in Fig. \ref{fig:controllerdisc}. 
%
%\begin{figure}[h]
%\includegraphics[width=0.4\textwidth]{controllerdisc}
%\centering
%\caption{Operating principle of a discharge protector (Source: \cite{Hansen})}
%\label{fig:controllerdisc}
%\end{figure}
%
%According to \cite{Lorenzo}, the switches may either be electromechanical (relay, contactors, etc.) or solid state (bipolar transistors, MOSFET's, etc.). 
%
%The steps in the modeling of the controller process are summarized in Table \ref{table:controller}.

@@

Where $ I_{DC} $ is the current required by the inverter from the DC source in order to be able to keep the rated voltage on the AC side, $ V_{DC} $ is the input voltage to the inverter delivered by the DC source (PV panel or battery),  $ V_{AC}  $ and $ I_{AC} $ are the output voltage and current, respectively, and $ cos \varphi $ can be found from the inverter's data-sheet.

@@

\subsection{ESBMC }
According \cite{GadelhaSBMF}, ESBMC is an open source, permissively licensed (Apache 2), cross platform bounded model checking for C and C++ programs. the efficient SMT based model checker, is a software verification tool for C and C++ code bases. Fig. \ref{fig:esbmcarch} shows the tool architecture.

@@

Finally, the system attempting to determine whether a formula, which is the disjunction of all possible errors, can be satisfied. If the SMT formula is shown to be satisfiable, a counterexample is presented; if the formula is found to be unsatisfiable, there are no errors up to the unwinding bound, and this result is presented.

@@

And related to the four 700 W PV system, the sizing check was successful, but there were  found flaws in everyone, all related with the SOC that reached levels below of 75\%. The framework identified the flaws right after the first night-discharge cycle, before dawn, and before the system start to recharge the batteries. The framework took 409.3 hours to found an error at house 1, and the maximum of 456XXX hours to house 4.

@@

\section{Conclusions and Future Work}
%The proposed framework seems to be a coherent and promising tool to perform verification of a PV project. The next step is the deployment of the solution at the ESBMC environment, and compare the results with a real PV project deployed at the field. 
%
%The framework presented here establishes the automated verification and the project sizing check. 
It was shown that, beside the time-consuming issue of the proposed framework, it overcomes the results of off-the-shelf tool that only simulate the results. The framework was successful in found sizing errors and to indicate in which conditions, in terms of temperature and solar irradiation, a PV system can fails.
%However, it is possible to perform the optimum sizing of the PV system. Moreover, 
%The authors target the use of Counterexample Guided-Inductive Synthesis (CEGIS) to perform the optimum sizing of PV systems. That is an interesting resource, considering that nowadays is possible to choose from many different manufacturers and many different models of equipment of a PV system. 
Next, the framework will be improved to start from a list of commercial equipment (inputs), where each equipment is verified during synthesis phase and the final solution, which satisfies the specifications (or constraints) of the project, is found from the inputs. This can be done with the Counterexample Guided-Inductive Synthesis (CEGIS), and the result is the optimum sizing of PV systems.

>>>>

\section{Introduction}
% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps.
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by the IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
% 
% Here we have the typical use of a "T" for an initial drop letter
% and "HIS" in caps to complete the first word.
\IEEEPARstart{A}{ccording} to Coelho et al. \cite{Coelho}, there are presently 1.3 billion people with no access to electricity worldwide. 
%The definition of energy access usually includes both electricity access and access to modern fuels for cooking and heating, in order to replace traditional biomass. 
%Increased access to energy allows economic growth and poverty alleviation \cite{Karekesi}. 
%
%Among the options of renewable sources, there are hydro, wind, and solar photovoltaic (PV). 
Only a niche market a few years ago, solar photovoltaic (PV) are now becoming a mainstream electricity provider.
% changing the way the world is powered. 
Based on data from \cite{EPIA}, there was an increase of approximately 50\% from 2016 to 2017 in terms of new installations of PV. 
%The use of the power generation technology with renewable energy source is developing rapidly due to the industrial development \cite{Yatimi}. 
%The renewable energy leads to an advance all over the world by protecting the environment: it is clean,
%(low greenhouse gases emissions)
%operating silently, long lifetime, low maintenance, absence of fuel cost and inexhaustible \cite{Noroozian}. 
%Renewable energy, and particularly the power generation from solar energy using photovoltaic (PV) panels, has emerged as an alternative to fossil or nuclear fuel generation.
% 
%The PV cell in a solar photovoltaic system, as defined in \cite{Rawat}, is a semiconductor device, which directly converts the solar radiation into electrical energy. 
%
%Apart from PV modules; the 
%PV systems consist of PV modules, battery bank, controller, and inverter, plus the load. %Moreover, the optimum sizing of these devices is important for reliable operation.
%Therefore, these systems need to be designed properly according to the site, land area available, load requirement, load pattern, environmental conditions and economics in order to utilize available resources efficiently and economically \cite{Rawat}. %Furthermore, there is the need for proper modeling and simulation tools for people involved in their application.

In order to validate or even simulate a potential PV solution, there are a myriad of tools available at the market, as RETScreen, HOMER, PVWatts, SAM, and Hybrid2.
%The increase in a number of PV systems installed all over the world brings the need for proper modeling and simulation tools for researcher and practitioners involved in their application. In order to validate or even simulate a potential PV solution, there are a myriad of tools. 
%However, to the best of our knowledge, this work can be the first work to perform automated verification of a solar PV off-grid project solution.  
%
%According to \cite{SEIA} and \cite{Chauhan}, solar is the most abundant source of renewable energy on earth. In SPV system, solar radiations are captured from the sun and turned into electricity using SPV cells made of silicon and other materials. SPV...
%
%In order to address different aspects of a SPV project, there is a myriad of public domain and commercial software available. According to \cite{Brooks}, the capabilities of these tools range from simple solar resource and energy production estimative, to site survey and system design tools, to complex financial analysis software (with optimization). Some tools also provide support to rebate programs applications and tax incentives (specific to each country or region), while other programs and worksheets focus on the technical aspects of system sizing and design.  
%
%Manufactures and integrators have yet their proprietary software to perform various system sizing, with the drawback of include just their own products among the possibilities of choice, what restrict the solution. 
%
%PV systems can be classified into grid-connected and stand-alone systems. At this proposal, only off-grid or stand-alone systems will be considered. The utilization of solar energy in off-grid mode has the potential to meet the energy need for remote rural areas of developing countries.  
However, those tools are based only in simulation models. The use of simulation for verification is problematic, because is necessary to ensure the complete coverage of operating conditions, scenarios, and system inputs.

Formal methods based on model checking offer great potential to obtain a more effective and faster verification in the design process. Programs may be viewed as mathematical objects. 
%with behavior that is, in principle, well determined. 
 This makes it possible to specify systems as programs using mathematical logic, which constitutes the intended (correct) behavior. Then, one can try to give a formal proof or otherwise establish that the program meets its specification. %, as defined by \cite{Trindade}. 
%
%This area of research is referred as formal methods. % as defined in \cite{Clarkeetal}.
% Their aim is to establish system correctness with mathematical rigor. 
%In the recent decades, research in formal methods has led to the development of very promising verification techniques.
% that facilitate the early detection of bugs in order to ensure the correctness of the system. 
%
%Model-based verification techniques are based on models that describe the possible system behavior in a mathematically precise and unambiguous manner. 
%Thus, such problems as incompleteness, ambiguities, and inconsistencies, which normally are discovered only in later stages of the design, can be detected in advance, as described by \cite{Trindade}. 
 Algorithms can verify the system model through systematically explore all their states.

@@

The results prove that the framework is more efficient in different case studies to find not proper functioning of PV systems than simulation with off-the-sheld tool. To the best of our knowledge, this is the first work to use a
%n SMT-based 
verification tool to solve this kind of problem. That is the main contribution of this paper.

@@

\section{Solar Photovoltaic System }
%According to \cite{Roy}, a 
A PV system is designed to give the electric supply to a load. This load can be either Alternate Current (AC) or Direct Current (DC) type. Electric supply can be needed either in daytime or evening time. 
%(in particular cases, in both times). %The most basic PV system can give supply only in daytime.  
For night hours or rainy days, one needed to have batteries, where power can be stored and used.% \cite{Gules}.

@@

\section{Design and Validation of a Solar photovoltaic system}
%The design and validation of a PV system can be done by hand or with the aid of a software tool. 
%
In order to address different aspects of project system and systems design, there is a myriad of tools. 
%public domain and commercial software available for the PV market. 
%According to \cite{Brooks}, t
The capabilities of these tools range from simple solar resource and energy production estimation, %to site survey and system design tools,
 to complex financial analysis and project optimization. 
%Some tools also provide support to rebate programs applications and tax incentives (specific to each country or region), while other programs and worksheets focus on the technical aspects of system sizing and design.
%
%Manufacturers and integrators have yet their proprietary software to perform inverter string sizing and various system sizing and design tools, with the drawback to just include their own products among the possibilities of choice. 
In this work, were evaluated the most popular tools, as PVWatts, SAM, HOMER Pro, RETScreen Expert, and Hybrid2.

@@

\subsection{Paper Proposal x Reference Tools}
Considering the focus of this paper, only HOMER remain for comparative. All tools need some parameters inherently from manufacturer's catalog in order to size the system.
%, so the project starts with manufacturers and integrators tool to define the basic items of the project: panels, inverters, controllers, and batteries. 
After that, the potential solution is analyzed in another tool to validate or even optimize the solution. Therefore, that is the challenge of this work, i.e., to prove that is possible to use automated verification to validate an off-grid PV solution and to prove that this verification is more efficient and complete than the listed-more common tools. The comparative between the HOMER Pro and the automated verification tool is presented at the Section \ref{sec:results}.

\section{Component models for stand-alone PV system }
%The main purpose of this section is to describe the models for the elements of a standalone PV system: PV generator, battery, controller, inverter, and load. 
The modeling of the PV system is based on modular blocks, as illustrated in Fig.\ref{fig:blockdiagram}. The modular structure facilitates the modeling of the other system structures and replacing of elements as, for instance, a DC load instead of an AC load.

@@

Where $ T_{air} $ is the ambient temperature, $NOCT$ is the nominal operating cell temperature (in $^{o}$C) that is find at the PV manufacturer's data-sheet, and $G$ is the solar irradiance ($ W/m^{2} $) of the place where the PV system is deployed.

@@

In \cite{Mellit} was established that the controller allows the management of energy between the load and the battery. 
%The input signals for regulator model are the battery current ($ I_{br} $), PV generator's voltage ($ V_{PV} $), PV generator's current ($ I_{PV} $), and battery voltage ($ V_{b} $). The outputs are battery ($ I_{rb} $) current and used current ($ I_{u} $). 
According \cite{Hansen}, to protect the battery against an excessive charge, the PV arrays are disconnected from the system, when the terminal voltage increases above a certain threshold $ V_{max \textunderscore off} $ and when the current required by the load is less than the current delivered by the PV arrays. PV arrays are connected again when the terminal voltage decreases below a certain value $ V_{max \textunderscore on} $. 
%This can be done by using a switch with a hysteresis cycle, as illustrated in Fig. \ref{fig:controllerover}. 
%
%\begin{figure}[h]
%\includegraphics[width=0.4\textwidth]{controllerover}
%\centering
%\caption{Operating principle of an overcharge protector (Source: \cite{Hansen})}
%\label{fig:controllerover}
%\end{figure}

To protect the battery against excessive discharge, the load is disconnected when the terminal voltage falls below a certain threshold $ V_{min \textunderscore off} $ and when the current required by the load is larger than the current delivered by the PV arrays \cite{Hansen}. The load is reconnected to the system, when the terminal voltage is above a certain value $ V_{min \textunderscore on} $.
%, using a switch with a hysteresis cycle, as shown in Fig. \ref{fig:controllerdisc}. 
%
%\begin{figure}[h]
%\includegraphics[width=0.4\textwidth]{controllerdisc}
%\centering
%\caption{Operating principle of a discharge protector (Source: \cite{Hansen})}
%\label{fig:controllerdisc}
%\end{figure}
%
%According to \cite{Lorenzo}, the switches may either be electromechanical (relay, contactors, etc.) or solid state (bipolar transistors, MOSFET's, etc.). 
%
The steps in the modeling of the controller process are summarized in Table \ref{table:controller}.

@@

Where $ I_{DC} $ is the current required by the inverter from the DC source in order to be able to keep the rated voltage on the AC side, $ V_{DC} $ is the input voltage to the inverter delivered by the DC source (PV panel or battery),  $ V_{AC}  $ and $ I_{AC} $ are the output voltage and current, respectively, and $ cos \varphi $ can be find from the inverter's data-sheet.

@@

\subsection{ESBMC }
According \cite{GadelhaSBMF}, ESBMC (or Efficient SMT-based Bounded Model Checker) is an open source, permissively licensed (Apache 2), cross platform bounded model checking for C and C++ programs. 
%The efficient SMT based model checker, is a software verification tool for C and C++ code bases. 
Fig. \ref{fig:esbmcarch} shows the tool architecture.

@@

Finally, the system attempting to determine whether a formula, which is the disjunction of all possible errors, can be satisfied. If the SMT formula is shown to be satisfiable, a counterexample is presented; if the formula is find to be unsatisfiable, there are no errors up to the unwinding bound, and this result is presented.

@@

And related to the four 700 W PV system, the sizing check was successful, but there were  found flaws in everyone, all related with the SOC that reached levels below of 75\%. The framework identified the flaws right after the first night-discharge cycle, before dawn, and before the system start to recharge the batteries. The framework took 409.3 hours to find an error at house 1, and the maximum of 456XXX hours to house 4.

@@

\section{Conclusions and Future Work}
%The proposed framework seems to be a coherent and promising tool to perform verification of a PV project. The next step is the deployment of the solution at the ESBMC environment, and compare the results with a real PV project deployed at the field. 
%
%The framework presented here establishes the automated verification and the project sizing check. 
It was shown that, beside the time-consuming issue of the proposed framework, it overcomes the results of off-the-shelf tool that only simulate the results. The framework was successful in find sizing errors and to indicate in which conditions, in terms of temperature and solar irradiation, a PV system can fails.
%However, it is possible to perform the optimum sizing of the PV system. Moreover, 
%The authors target the use of Counterexample Guided-Inductive Synthesis (CEGIS) to perform the optimum sizing of PV systems. That is an interesting resource, considering that nowadays is possible to choose from many different manufacturers and many different models of equipment of a PV system. 
Next, the framework will be improved to start from a list of commercial equipment (inputs), where each equipment is verified during synthesis phase and the final solution, which satisfies the specifications (or constraints) of the project, is find from the inputs. This can be done with the Counterexample Guided-Inductive Synthesis (CEGIS), and the result is the optimum sizing of PV systems.
